\documentclass{article}
\usepackage{graphicx} % Required for inserting images
\usepackage[utf8]{inputenc}
\usepackage{parskip} % Adds space between paragraphs (more readable)
\usepackage{geometry}
\geometry{margin=1in}

\title{\centering HealthGuard - Smart Cardiac Health Monitoring System}
\author{
    Sadim Rahman Badhan \\
    Deepak Kapil \\
    Turja Barua \\
    Muhammed Aamir Ejaz Ejaz
}
\date{}

\begin{document}

\maketitle

\section*{Executive Summary – Aamir}

% Add Aamir's content here

\section*{Product Presentation – Turja Barua}

% Add Turja's content here

\section*{Marketing Strategy – Deepak}

% Add Deepak's content here


\subsection*{\centering Organizational Development and Insights}
\subsubsection*{\centering Our Startup Journey}

HealthGuard, our startup, aims to help patients with severe heart conditions by providing a device that will not only help them keep track of their condition and stay in touch with doctors, but also offer psychological comfort by assuring them that they are being closely monitored and are not alone. Having a serious illness can drain a patient not only physically but also psychologically.

Our mission is to save lives through prompt action and proper monitoring, allowing doctors to keep an eye on their severely ill patients and take necessary action in case of an emergency or abnormal cardiac behaviour. This is why, as a team, we decided to build a software system that is intelligent enough to monitor heart conditions by constantly checking heart rate and blood oxygen levels, identifying abnormal heart rates that are not related to physical exercise, and, based on the situation, taking appropriate action such as organizing a check-up with a doctor or contacting emergency services, which could be life-saving for a patient.

We, as a team, recognized the importance of hiring experienced professionals early on, especially to support our AI-powered health monitoring solution. We discussed and created a descriptive job ad that not only outlined our technical requirements but also emphasized curiosity and a solution-oriented mindset. The ad highlighted familiarity with deep learning techniques and experience working with wearable APIs or hardware for better system optimization. It was clear and concise about our expectations and gave a strong overview of our startup's mission and benefits, helping us attract the right candidates.

Our job ad was posted on our student Moodle platform, where we received a significant number of applications. Each applicant's credentials were reviewed by both an AI tool and all team members to ensure they were qualified for the role. Upon agreement from the whole team, a candidate was selected and invited for an interview.

During the interview, we noticed there was a slight misunderstanding from the candidate regarding the role requirements, which we quickly clarified. The rest of the interview proceeded smoothly. As a team, we had an in-depth discussion, compared our notes, and decided on the candidate we would hire. Our main emphasis was on technical skills and a solution-oriented mindset, both of which the candidate demonstrated strongly during the interview.

This entire process taught us that when communicating our business, it is essential to have well-defined goals and clear role requirements that are accurately reflected in our talent acquisition strategy and all further communication.

\end{document}
